Cover Letter: Cudele (Paper 306)

### 2018-02-22 paper/sections/7_conclusion.tex
paper: camera ready template and squeeze to 10 pgs
Signed-off-by: Michael Sevilla <mikesevilla3@gmail.com>

Relaxing consistency/durability semantics in file systems is a double-edged
sword. While the technique performs and scales better, it alienates applications that rely
on strong consistency and durability.  Cudele lets
\oldcomment{users}\newcomment{administrators} assign consistency/durability
guarantees to subtrees in the global namespace, resulting in 
custom fit semantics for applications. We show how applications can co-exist and
perform well in a global namespace and our prototype enables studies that
adjust these semantics over {\it time and space}, where subtrees can change
without ever moving the data they reference.

%This approach is superior to mounting different storage systems in a global
%namespace because there is no need to provision dedicated storage clusters to
%applications or move data between these systems.  
Cudele prompts many avenues for future work.  First is to co-locate HPC
workflows with real highly parallel runtimes from the cloud in the same
namespace. This setup shows how Cudele reasonably incorporates both programming
models (client-driven parallelism and user-defined workflows) at the same time
and should show large performance gains.  Second is dynamically changing
semantics of a subtree from stronger to weaker guarantees (or vice versa). This
reduces data movement across storage cluster and file system boundaries so
the results of a Hadoop job do not need to be migrated into CephFS for
other processing; instead the \oldcomment{user}\newcomment{administrator} can
change the semantics of the HDFS subtree into a CephFS subtree, which may cause
metadata/data movement to ensure strong consistency. Third is embeddable
policies, where child subtrees have specialized features but still maintain
guarantees of their parent subtrees.  For example, a RAMDisk subtree is POSIX
IO-compliant but relaxes durability constraints, so it can reside under a POSIX
IO subtree alongside a globally durable subtree.

>>>>

Relaxing consistency/durability semantics in file systems is a double-edged
sword. While the technique performs and scales better, it alienates applications that rely
on strong consistency and durability.  Cudele lets
\oldcomment{users}\newcomment{administrators} assign consistency/durability
guarantees to subtrees in the global namespace, resulting in 
custom fit semantics for applications. We show how applications can co-exist and
perform well in a global namespace and our prototype enables studies that
adjust these semantics over {\it time and space}, where subtrees can change
without moving data they reference.`

%This approach is superior to mounting different storage systems in a global
%namespace because there is no need to provision dedicated storage clusters to
%applications or move data between these systems.  
\textbf{Future Work}: First is to co-locate HPC workflows with real highly
parallel runtimes from the cloud in the same namespace. This setup would show
how Cudele reasonably incorporates both programming models at the same time.
Second is dynamically changing semantics of a subtree from stronger to weaker
guarantees. This reduces data movement across storage cluster and file system
boundaries so the results of a Hadoop job do not need to be migrated into
CephFS for other processing; instead the
\oldcomment{user}\newcomment{administrator} can change the semantics of the
HDFS subtree into a CephFS subtree. Third is embeddable policies, where child
subtrees have specialized features but still maintain guarantees of the
parent subtree.  For example, a RAMDisk subtree is POSIX IO-compliant but
relaxes durability, so it can reside under a POSIX IO subtree
alongside a globally durable subtree.\vspace{-1ex}
